---
title: " "
output:
   html_document:
     css: style.css
---



<font size="5"> Data analysis for: </font>

<p align = "justify">
<font size="4"> Padilla Perez, D.J. & Angilletta Jr., M.J. (2022). Macroclimatic and maternal effects on the evolution of reproductive traits in lizards. *Ecology and Evolution*.</font>
</p>


</p></p>

[Dylan J. Padilla Perez](https://dylanpadilla.netlify.app/), School of Life Sciences, Arizona State University, Tempe, AZ 85287, USA.
</p></p>


<b>
<font size="4"> Library </font>
</b>

```{r,  echo = TRUE, warning = FALSE, message = FALSE}

require(geiger)
require(caper)
require(phylopath)
require(ggplot2)
require(ggtree)
require(ggtreeExtra)
require(gridExtra)
require(grid)
require(ggraph)
require(kableExtra)

```

```{r, warning = FALSE, comment = " "}
R.version
```

```{r,  echo = TRUE, warning = FALSE, comment = " "}

data <- read.csv("sites.csv", row.names = 1)
data_bt <- read.csv("sps_body_temp.csv", row.names = 1)
qgis_data <- read.csv("qgis_data.csv", row.names = 1)
tree <- read.tree("tree.nex")

colnames(qgis_data)[1] <- "Binomial"
mer_data <- merge(qgis_data, data, by = "Binomial")
mer_data <- na.omit(mer_data)
rownames(mer_data) <- mer_data$Binomial

mer2 <- merge(data_bt, qgis_data, by = "Binomial")
mer2 <- na.omit(mer2)
rownames(mer2) <- mer2$Binomial
head(mer2)

tapply(data$annual_temp, data$Family, length)
tapply(mer_data$annual_temp, mer_data$Family, length)
tapply(mer2$female.SVL, mer2$Family, length)


## Environmental temperature dataset

n1 <- mer_data[mer_data$Family != "Amphisbaenidae", ]


## Body temperature data

b1 <- mer2[mer2$Family != "Amphisbaenidae", ]
dat <- (n1)


dat$mclutch <- (dat$smallest.mean.clutch.size + dat$largest.mean.clutch.size) / 2


## Data for the Phylogeny

n2 <- data[data$Family != "Amphisbaenidae", ]
dtree <- n2
names(dtree)

dtree$mclutch <- (dtree$smallest.mean.clutch.size + dtree$largest.mean.clutch.size) / 2


check_t <- name.check(tree, dtree)
rm_phy_t <- check_t$tree_not_data
rm_dat_t <- check_t$data_not_tree
ctree_t <- drop.tip(tree, rm_phy_t)
dtree <- subset(dtree, subset = dtree$Binomial %in% ctree_t$tip, select = names(dtree)[1:19])
name.check(ctree_t, dtree)
ctree_t

```


```{r, echo = TRUE, warning = FALSE, comment = " ", fig.align = "center", fig.height = 7, fig.width = 7}

p <- ggtree(ctree_t, layout='circular', colour = "purple")


p + geom_fruit(data=dtree, geom=geom_bar, mapping=aes(x=log(female.SVL), y = Binomial, fill = "Maternal length (mm)"), pwidth = 0.1, stat="identity", orientation="y", colour = "#FDED95") + geom_fruit(data=dtree, geom=geom_bar, mapping=aes(x=hatchling.neonate.SVL, y = Binomial, fill = "Hatchling length (mm)"), pwidth = 0.1, stat="identity", orientation="y", colour = "#A0E3FE") + geom_fruit(data=dtree, geom=geom_bar, mapping=aes(x=mclutch, y = Binomial, fill = "Clutch size"), pwidth = 0.07, stat="identity", orientation="y", colour = "#FE97BA") + scale_fill_manual(values=c("#FE97BA", "#A0E3FE", "#FDED95"), guide=guide_legend(keywidth=0.5, keyheight=0.5, order=6, title = "")) + theme(legend.position=c(0.59, 0.461), legend.title=element_text(size=0), legend.text=element_text(size=6), legend.spacing.x = unit(0.06, "cm"))

```
<p align="justify">
<font size="4"> **Figure 3.** Evolution of the reproductive output among 669 species of lizards. The dataset used to perform path analyses was reduced to 486 species because we could not extract data of climatic variables for all species present in the phylogeny.</font>
</p>
<br><br><br>



```{r, echo = TRUE, warning = FALSE, comment = " ", fig.align = "center", fig.height = 7, fig.width = 7}

dat_bt_diurnal <- (b1)


dat_bt_diurnal$mclutch <- (dat_bt_diurnal$smallest.mean.clutch.size + dat_bt_diurnal$largest.mean.clutch.size) / 2

dat_bt_diurnal$mean_bt <- (dat_bt_diurnal$minimum.mean.Tb + dat_bt_diurnal$maximum.mean.Tb) / 2

dat_bt_diurnal <- na.omit(dat_bt_diurnal)

tapply(dat_bt_diurnal$female.SVL, dat_bt_diurnal$Family, length)
names(dat_bt_diurnal)


## Cheking whether the species names macth the tips of the tree

check <- name.check(tree, dat)
rm_phy <- check$tree_not_data
rm_dat <- check$data_not_tree

check_bt_diurnal <- name.check(tree, dat_bt_diurnal)
rm_phy_bt_diurnal <- check_bt_diurnal$tree_not_data
rm_dat_bt_diurnal <- check_bt_diurnal$data_not_tree


## Droping species names from the phylogeny

ctree <- drop.tip(tree, rm_phy)
ctree_bt_diurnal <- drop.tip(tree, rm_phy_bt_diurnal)

cdat <- subset(dat, subset = dat$Binomial %in% ctree$tip, select = names(dat)[1:30])
name.check(ctree, cdat)
names(cdat)
names(cdat)[c(17, 18, 30, 7, 11, 9)] <- c("FS", "HS", "CS", "ET", "PP", "PR")


cdat$PR <- log1p(cdat$PR)
cdat$PP <- log1p(cdat$PP)
cdat <- na.omit(cdat)

check <- name.check(tree, cdat)
rm_phy <- check$tree_not_data
rm_dat <- check$data_not_tree
ctree <- drop.tip(tree, rm_phy)
name.check(ctree, cdat)
str(cdat)


cdat_bt_diurnal <- subset(dat_bt_diurnal, subset = dat_bt_diurnal$Binomial %in% ctree_bt_diurnal$tip, select = names(dat_bt_diurnal)[1:32])
name.check(ctree_bt_diurnal, cdat_bt_diurnal)
names(cdat_bt_diurnal)
names(cdat_bt_diurnal)[c(5, 6, 31, 32, 29, 27)] <- c("FS", "HS", "CS", "BT", "PP", "PR")

cdat_bt_diurnal$PR <- log1p(cdat_bt_diurnal$PR)
cdat_bt_diurnal$PP <- log(cdat_bt_diurnal$PP)

cdat_bt_diurnal <- na.omit(cdat_bt_diurnal)

check_bt_diurnal <- name.check(tree, cdat_bt_diurnal)
rm_phy_bt_diurnal <- check_bt_diurnal$tree_not_data
rm_dat_bt_diurnal <- check_bt_diurnal$data_not_tree
ctree_bt_diurnal <- drop.tip(tree, rm_phy_bt_diurnal)
name.check(ctree_bt_diurnal, cdat_bt_diurnal)

str(cdat_bt_diurnal)

```


```{r,  echo = TRUE, warning = FALSE, message = FALSE, comment = " ", fig.align = "center", fig.height = 7, fig.width = 7}


ml3 <- define_model_set(
    null = c(),
    "(a)" = c(HS ~ ET),
    "(b)" = c(FS ~ ET),
    "(c)" = c(FS ~ ET, HS ~ ET),
    "(d)" = c(FS ~ PP),
    "(e)" = c(FS ~ PR),
    "(f)" = c(HS ~ PR),
    "(g)" = c(FS ~ PR, HS ~ PR),
    "(h)" = c(FS ~ PP + PR + ET, HS ~ ET, HS ~ PR),
    .common = c(CS ~ FS + HS, HS ~ FS, ET ~ PR, PP ~ ET, PP ~ PR))



ml4 <- define_model_set(
    null = c(),
    "(a)" = c(HS ~ BT),
    "(b)" = c(FS ~ BT),
    "(c)" = c(FS ~ BT, HS ~ BT),
    "(d)" = c(FS ~ PP),
    "(e)" = c(FS ~ PR),
    "(f)" = c(HS ~ PR),
    "(g)" = c(FS ~ PR, HS ~ PR),
    "(h)" = c(FS ~ PP + PR + BT, HS ~ BT, HS ~ PR),
    .common = c(CS ~ FS + HS, HS ~ FS, BT ~ PR, BT ~ PP, PP ~ PR))


```


```{r, results = "asis", echo = TRUE, fig.align = "center", fig.height = 7, fig.width = 7}


set_graph_style(family = "Times New Roman")

positions <- data.frame(name = c('PP', 'PR', 'ET', 'FS', 'HS', '', 'CS'), x = c(2:3, c(2.5, 1.75, 3.25, 2), 2.5), y = c(3, 3, 2.3, 2, 2, 2, 1))

plot_model_set(ml3, manual_layout = positions, text_size = 3, edge_width = 0.7)


mo <- phylo_path(ml3, cdat, ctree)
s <- summary(mo)
theme_set(theme_bw())
plot(s)

```

<b>
<font size="4"> Table S1.</font>
</b>


```{r, results = "asis", echo = TRUE, fig.align = "center", fig.height = 7, fig.width = 7}

kable(summary(mo)[ , 2:9], digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, position = "center")

```


```{r, results = "asis", echo = TRUE, fig.align = "center", fig.height = 7, fig.width = 7}


positions.bt <- data.frame(name = c('PP', 'PR', 'BT', 'FS', 'HS', '', 'CS'), x = c(2:3, c(2.6, 1.75, 3.25, 2), 2.5), y = c(3, 3, 2.2, 2, 2, 2, 1))

set_graph_style(family = "Times New Roman")


plot_model_set(ml4, manual_layout = positions.bt, text_size = 3, edge_width = 0.7)
```
<p align = "justify">
<font size="4"> **Figure 1.** Path models depicting relationships among body temperature and life-history traits derived from optimality models (see text for details). Abbreviation in the path diagrams are as follows: BT = body temperature; CS = clutch size; FS = maternal length; HS = hatchling/neonate length; PP = primary production; PR = annual precipitation.</font>
</p>

<br><br><br>


```{r, results = "asis", echo = TRUE, fig.align = "center", fig.height = 7, fig.width = 7}

mo_bt_diurnal <- phylo_path(ml4, cdat_bt_diurnal, ctree_bt_diurnal)
s.bt <- summary(mo_bt_diurnal)
theme_set(theme_bw())
plot(s.bt)

```
<p align = "justify">
<font size="4"> **Figure 4.** Relative importance of the causal models describing the evolution of reproductive traits in lizards.</font>
</p>

<br><br><br>



<font size="4"> **Table S2.**</font>

```{r, results = "asis", echo = TRUE, fig.align = "center", fig.height = 7, fig.width = 7}

kable(summary(mo_bt_diurnal)[ , 2:9], digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, position = "center")

```



```{r, echo = TRUE, warning = FALSE, comment = " ", fig.align = "center", fig.height = 7, fig.width = 7}

mo$d_sep

mo_bt_diurnal$d_sep

```

<br><br><br>

<b>
<font size="4"> Model averaging </font>
</b>

<br><br><br>

```{r, echo = TRUE, warning = FALSE, comment = " ", fig.align = "center", fig.height = 7, fig.width = 7}


avg <- average(mo, avg_method = "full", cut_off = 2)
avg

avg_bt_diurnal <- average(mo_bt_diurnal, avg_method = "full", cut_off = 2)
avg_bt_diurnal

```


```{r, echo = TRUE, message = FALSE, comment = "", warning = FALSE, fig.align = "center", fig.height = 7, fig.width = 7}


set_graph_style(family = "Times New Roman", text_size = 12)

d2 <- plot(avg_bt_diurnal, manual_layout = positions.bt, text_size = 4.2, edge_width = 0.05, curvature = -0, colors = c("brown", "black")) + ggplot2::scale_x_continuous(expand = c(0.2, 0)) + ggplot2::scale_y_continuous(expand = c(0.1, 0)) + theme(plot.margin=unit(c(0, 0, 0, 0), "cm")) + theme(legend.text = element_text(size = 13, family = "serif")) + theme(plot.title = element_text(size = 14, family = "serif", face = "bold")) + annotate(geom = "text", x = 2.74, y = 2.07, angle = 0, label = "(±0.02)", size = 3.8) + annotate(geom = "text", angle = 300, x = 2.33, y = 1.38, label = "(±0.09)", size = 3.8) + annotate(geom = "text", x = 3.06, y = 1.63, angle = 59, label = "(±0.10)", size = 3.8) + ggtitle("n = 320") + theme(plot.title = element_text(hjust = 0.566, vjust = -10), legend.position = "none")

d3 <- plot(avg, manual_layout = positions, text_size = 4.2, edge_width = 0.05, curvature = -0, colors = c("brown", "black")) + ggplot2::scale_x_continuous(expand = c(0.2, 0)) + ggplot2::scale_y_continuous(expand = c(0.1, 0)) + theme(plot.margin=unit(c(0, 0, 0, 0), "cm")) + theme(legend.text = element_text(size = 13, family = "serif")) + theme(plot.title = element_text(size = 14, family = "serif", face = "bold")) + annotate(geom = "text", x = 2.74, y = 2.07, angle = 0, label = "(±0.02)", size = 3.8) + annotate(geom = "text", angle = 300, x = 2.33, y = 1.38, label = "(±0.08)", size = 3.8) + annotate(geom = "text", x = 3.06, y = 1.63, angle = 59, label = "(±0.09)", size = 3.8) + theme(plot.title = element_text(hjust = 0.57, vjust = -10), legend.position = "none") + ggtitle("n = 439")


grob <- grobTree(textGrob("(a)", x = 0.09,  y = 0.97, hjust = 0, gp = gpar(fontsize = 12, fontface = "bold", fontfamily = "Times New Roman")))

grob2 <- grobTree(textGrob("(b)", x = 0.09,  y = 0.97, hjust = 0, gp = gpar(fontsize = 12, fontface = "bold", fontfamily = "Times New Roman")))

c1 <- d2 + annotate(geom = "text", x = 2.73, y = 2.934, angle = 0, label = "(±0.02)", size = 3.8) + annotate(geom = "text", x = 3.26, y = 2.324, angle = 280, label = "(±0.02)", size = 3.8) + annotate(geom = "text", x = 2.26, y = 2.57, angle = 298, label = "(±0.08)", size = 3.8) + annotate(geom = "text", x = 2.95, y = 2.75, angle = 72, label = "(±0.08)", size = 3.8) + annotate(geom = "text", x = 2.58, y = 2.59, angle = 48, label = "(±0.04)", size = 3.8) + annotate(geom = "text", x = 1.6, y = 3, label = "(a)", size = 5, fontface = 2)

c2 <- d3 + annotate(geom = "text", x = 2.73, y = 2.934, angle = 0, label = "(±0.02)", size = 3.8) + annotate(geom = "text", x = 3.26, y = 2.324, angle = 278, label = "(±0.02)", size = 3.8) + annotate(geom = "text", x = 2.28, y = 2.69, angle = 298, label = "(±0.02)", size = 3.8) + annotate(geom = "text", x = 2.92, y = 2.78, angle = 66, label = "(±0.04)", size = 3.8) + annotate(geom = "text", x = 2.58, y = 2.59, angle = 48, label = "(±0.02)", size = 3.8) + annotate(geom = "text", x = 1.6, y = 3, label = "(b)", size = 5, fontface = 2)

quartz()
grid.arrange(grobs = list(c1, c2), ncol = 2, vp = viewport(width = 1.1, height = 0.8), layout_matrix = rbind(c(1, 2), c(1, 2)))



```
<p align = "justify">
<font size="4"> **Figure 2.** Best-fit models of the evolution of reproductive traits considering body temperature (a) and environmental temperature (b) as independent variable. Thicker arrows indicate stronger effects. Values in parentheses denote the standard errors of the path coefficients.</font>
</p>




<br><br><br><br><br><br><br><br><br><br><br>

<p align = "justify">
<font size="4"> **The following section consists of the same analyses but, this time, we use female mass and hatchling mass as measures of maternal size and hatchling size.**</font>
</p>

<br><br><br>

```{r,  echo = TRUE, warning = FALSE, comment = " "}


rm(list = ls())



data <- read.csv("sites.csv", row.names = 1)
data_bt <- read.csv("sps_body_temp.csv", row.names = 1)
qgis_data <- read.csv("qgis_data.csv", row.names = 1)
tree <- read.tree("tree.nex")

colnames(qgis_data)[1] <- "Binomial"
mer_data <- merge(qgis_data, data, by = "Binomial")
mer_data <- na.omit(mer_data)
rownames(mer_data) <- mer_data$Binomial

mer2 <- merge(data_bt, qgis_data, by = "Binomial")
mer2 <- na.omit(mer2)
rownames(mer2) <- mer2$Binomial
head(mer2)

tapply(data$annual_temp, data$Family, length)
tapply(mer_data$annual_temp, mer_data$Family, length)
tapply(mer2$female.SVL, mer2$Family, length)


## Environmental temperature dataset

n1 <- mer_data[mer_data$Family != "Amphisbaenidae", ]


## Body temperature data

b1 <- mer2[mer2$Family != "Amphisbaenidae", ]
dat <- (n1)


dat$mclutch <- (dat$smallest.mean.clutch.size + dat$largest.mean.clutch.size) / 2
tapply(dat$annual_temp, dat$Family, length)
str(dat)


## Data for the Phylogeny

n2 <- data[data$Family != "Amphisbaenidae", ]
dtree <- n2
names(dtree)

dtree$mclutch <- (dtree$smallest.mean.clutch.size + dtree$largest.mean.clutch.size) / 2


check_t <- name.check(tree, dtree)
rm_phy_t <- check_t$tree_not_data
rm_dat_t <- check_t$data_not_tree
ctree_t <- drop.tip(tree, rm_phy_t)
dtree <- subset(dtree, subset = dtree$Binomial %in% ctree_t$tip, select = names(dtree)[1:19])
name.check(ctree_t, dtree)
ctree_t

```


```{r, echo = TRUE, warning = FALSE, comment = " ", fig.align = "center", fig.height = 7, fig.width = 7}

p <- ggtree(ctree_t, layout='circular', colour = "purple")


p + geom_fruit(data=dtree, geom=geom_bar, mapping=aes(x=log(female_mass), y = Binomial, fill = "Maternal mass (g)"), pwidth = 0.1, stat="identity", orientation="y", colour = "#FDED95") + geom_fruit(data=dtree, geom=geom_bar, mapping=aes(x=log(hatchling_mass), y = Binomial, fill = "Hatchling mass (g)"), pwidth = 0.1, stat="identity", orientation="y", colour = "#A0E3FE") + geom_fruit(data=dtree, geom=geom_bar, mapping=aes(x=mclutch, y = Binomial, fill = "Clutch size"), pwidth = 0.07, stat="identity", orientation="y", colour = "#FE97BA") + scale_fill_manual(values=c("#FE97BA", "#A0E3FE", "#FDED95"), guide=guide_legend(keywidth=0.5, keyheight=0.5, order=6, title = "")) + theme(legend.position=c(0.59, 0.461), legend.title=element_text(size=0), legend.text=element_text(size=6), legend.spacing.x = unit(0.06, "cm"))

```


```{r, echo = TRUE, warning = FALSE, comment = " ", fig.align = "center", fig.height = 7, fig.width = 7}

dat_bt_diurnal <- (b1)


dat_bt_diurnal$mclutch <- (dat_bt_diurnal$smallest.mean.clutch.size + dat_bt_diurnal$largest.mean.clutch.size) / 2

dat_bt_diurnal$mean_bt <- (dat_bt_diurnal$minimum.mean.Tb + dat_bt_diurnal$maximum.mean.Tb) / 2

dat_bt_diurnal <- na.omit(dat_bt_diurnal)

tapply(dat_bt_diurnal$female.SVL, dat_bt_diurnal$Family, length)
names(dat_bt_diurnal)


## Cheking whether the species names macth the tips of the tree

check <- name.check(tree, dat)
rm_phy <- check$tree_not_data
rm_dat <- check$data_not_tree

check_bt_diurnal <- name.check(tree, dat_bt_diurnal)
rm_phy_bt_diurnal <- check_bt_diurnal$tree_not_data
rm_dat_bt_diurnal <- check_bt_diurnal$data_not_tree


## Droping species names from the phylogeny

ctree <- drop.tip(tree, rm_phy)
ctree_bt_diurnal <- drop.tip(tree, rm_phy_bt_diurnal)

cdat <- subset(dat, subset = dat$Binomial %in% ctree$tip, select = names(dat)[1:30])
name.check(ctree, cdat)
names(cdat)
names(cdat)[c(21, 22, 30, 7, 11, 9)] <- c("FS", "HS", "CS", "ET", "PP", "PR")


cdat$PR <- log1p(cdat$PR)
cdat$PP <- log1p(cdat$PP)
cdat <- na.omit(cdat)

check <- name.check(tree, cdat)
rm_phy <- check$tree_not_data
rm_dat <- check$data_not_tree
ctree <- drop.tip(tree, rm_phy)
name.check(ctree, cdat)
str(cdat)


cdat_bt_diurnal <- subset(dat_bt_diurnal, subset = dat_bt_diurnal$Binomial %in% ctree_bt_diurnal$tip, select = names(dat_bt_diurnal)[1:32])
name.check(ctree_bt_diurnal, cdat_bt_diurnal)
names(cdat_bt_diurnal)
names(cdat_bt_diurnal)[c(9, 10, 31, 32, 29, 27)] <- c("FS", "HS", "CS", "BT", "PP", "PR")

cdat_bt_diurnal$PR <- log1p(cdat_bt_diurnal$PR)
cdat_bt_diurnal$PP <- log(cdat_bt_diurnal$PP)

cdat_bt_diurnal <- na.omit(cdat_bt_diurnal)

check_bt_diurnal <- name.check(tree, cdat_bt_diurnal)
rm_phy_bt_diurnal <- check_bt_diurnal$tree_not_data
rm_dat_bt_diurnal <- check_bt_diurnal$data_not_tree
ctree_bt_diurnal <- drop.tip(tree, rm_phy_bt_diurnal)
name.check(ctree_bt_diurnal, cdat_bt_diurnal)

str(cdat_bt_diurnal)

```


```{r,  echo = TRUE, warning = FALSE, message = FALSE, comment = " ", fig.align = "center", fig.height = 7, fig.width = 7}


ml3 <- define_model_set(
    null = c(),
    "(a)" = c(HS ~ ET),
    "(b)" = c(FS ~ ET),
    "(c)" = c(FS ~ ET, HS ~ ET),
    "(d)" = c(FS ~ PP),
    "(e)" = c(FS ~ PR),
    "(f)" = c(HS ~ PR),
    "(g)" = c(FS ~ PR, HS ~ PR),
    "(h)" = c(FS ~ PP + PR + ET, HS ~ ET, HS ~ PR),
    .common = c(CS ~ FS + HS, HS ~ FS, ET ~ PR, PP ~ ET, PP ~ PR))



ml4 <- define_model_set(
    null = c(),
    "(a)" = c(HS ~ BT),
    "(b)" = c(FS ~ BT),
    "(c)" = c(FS ~ BT, HS ~ BT),
    "(d)" = c(FS ~ PP),
    "(e)" = c(FS ~ PR),
    "(f)" = c(HS ~ PR),
    "(g)" = c(FS ~ PR, HS ~ PR),
    "(h)" = c(FS ~ PP + PR + BT, HS ~ BT, HS ~ PR),
    .common = c(CS ~ FS + HS, HS ~ FS, BT ~ PR, BT ~ PP, PP ~ PR))


```


```{r, results = "asis", echo = TRUE, fig.align = "center", fig.height = 7, fig.width = 7}


positions <- data.frame(name = c('PP', 'PR', 'ET', 'FS', 'HS', '', 'CS'), x = c(2:3, c(2.5, 1.75, 3.25, 2), 2.5), y = c(3, 3, 2.3, 2, 2, 2, 1))

mo <- phylo_path(ml3, cdat, ctree)
s <- summary(mo)
theme_set(theme_bw())
plot(s)

```

<b>
<font size="4"> Table S3.</font>
</b>


```{r, results = "asis", echo = TRUE, fig.align = "center", fig.height = 7, fig.width = 7}

kable(summary(mo)[ , 2:9], digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, position = "center")

```



```{r, results = "asis", echo = TRUE, fig.align = "center", fig.height = 7, fig.width = 7}


positions.bt <- data.frame(name = c('PP', 'PR', 'BT', 'FS', 'HS', '', 'CS'), x = c(2:3, c(2.6, 1.75, 3.25, 2), 2.5), y = c(3, 3, 2.2, 2, 2, 2, 1))

mo_bt_diurnal <- phylo_path(ml4, cdat_bt_diurnal, ctree_bt_diurnal)
s.bt <- summary(mo_bt_diurnal)
theme_set(theme_bw())
plot(s.bt)

```

<font size="4"> **Table S4.**</font>

```{r, results = "asis", echo = TRUE, fig.align = "center", fig.height = 7, fig.width = 7}

kable(summary(mo_bt_diurnal)[ , 2:9], digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, position = "center")

```



```{r, echo = TRUE, warning = FALSE, comment = " ", fig.align = "center", fig.height = 7, fig.width = 7}

mo$d_sep

mo_bt_diurnal$d_sep

```

<br><br><br>

<b>
<font size="4"> Model averaging </font>
</b>

<br><br><br>

```{r, echo = TRUE, warning = FALSE, comment = " ", fig.align = "center", fig.height = 7, fig.width = 7}


avg <- average(mo, avg_method = "full", cut_off = 2)
avg

avg_bt_diurnal <- average(mo_bt_diurnal, avg_method = "full", cut_off = 2)
avg_bt_diurnal

```


```{r, echo = TRUE, message = FALSE, comment = "", warning = FALSE, fig.align = "center", fig.height = 7, fig.width = 7}


set_graph_style(family = "Times New Roman", text_size = 12)

d2 <- plot(avg_bt_diurnal, manual_layout = positions.bt, text_size = 4.2, edge_width = 0.05, curvature = -0, colors = c("brown", "black")) + ggplot2::scale_x_continuous(expand = c(0.2, 0)) + ggplot2::scale_y_continuous(expand = c(0.1, 0)) + theme(plot.margin=unit(c(0, 0, 0, 0), "cm")) + theme(legend.text = element_text(size = 13, family = "serif")) + theme(plot.title = element_text(size = 14, family = "serif", face = "bold")) + annotate(geom = "text", x = 2.74, y = 2.07, angle = 0, label = "", size = 3.8) + annotate(geom = "text", angle = 300, x = 2.33, y = 1.38, label = "", size = 3.8) + annotate(geom = "text", x = 3.06, y = 1.63, angle = 59, label = "", size = 3.8) + ggtitle("n = 320") + theme(plot.title = element_text(hjust = 0.566, vjust = -10), legend.position = "none")

d3 <- plot(avg, manual_layout = positions, text_size = 4.2, edge_width = 0.05, curvature = -0, colors = c("brown", "black")) + ggplot2::scale_x_continuous(expand = c(0.2, 0)) + ggplot2::scale_y_continuous(expand = c(0.1, 0)) + theme(plot.margin=unit(c(0, 0, 0, 0), "cm")) + theme(legend.text = element_text(size = 13, family = "serif")) + theme(plot.title = element_text(size = 14, family = "serif", face = "bold")) + annotate(geom = "text", x = 2.74, y = 2.07, angle = 0, label = "", size = 3.8) + annotate(geom = "text", angle = 300, x = 2.33, y = 1.38, label = "", size = 3.8) + annotate(geom = "text", x = 3.06, y = 1.63, angle = 59, label = "", size = 3.8) + theme(plot.title = element_text(hjust = 0.57, vjust = -10), legend.position = "none") + ggtitle("n = 439")


grob <- grobTree(textGrob("(a)", x = 0.09,  y = 0.97, hjust = 0, gp = gpar(fontsize = 12, fontface = "bold", fontfamily = "Times New Roman")))

grob2 <- grobTree(textGrob("(b)", x = 0.09,  y = 0.97, hjust = 0, gp = gpar(fontsize = 12, fontface = "bold", fontfamily = "Times New Roman")))

c1 <- d2 + annotate(geom = "text", x = 2.73, y = 2.934, angle = 0, label = "", size = 3.8) + annotate(geom = "text", x = 3.26, y = 2.324, angle = 280, label = "", size = 3.8) + annotate(geom = "text", x = 2.26, y = 2.57, angle = 298, label = "", size = 3.8) + annotate(geom = "text", x = 2.95, y = 2.75, angle = 72, label = "", size = 3.8) + annotate(geom = "text", x = 2.58, y = 2.59, angle = 48, label = "", size = 3.8) + annotate(geom = "text", x = 1.6, y = 3, label = "(a)", size = 5, fontface = 2)

c2 <- d3 + annotate(geom = "text", x = 2.73, y = 2.934, angle = 0, label = "", size = 3.8) + annotate(geom = "text", x = 3.26, y = 2.324, angle = 278, label = "", size = 3.8) + annotate(geom = "text", x = 2.28, y = 2.69, angle = 298, label = "", size = 3.8) + annotate(geom = "text", x = 2.92, y = 2.78, angle = 66, label = "", size = 3.8) + annotate(geom = "text", x = 2.58, y = 2.59, angle = 48, label = "", size = 3.8) + annotate(geom = "text", x = 1.6, y = 3, label = "(b)", size = 5, fontface = 2)

quartz()
grid.arrange(grobs = list(c1, c2), ncol = 2, vp = viewport(width = 1.1, height = 0.8), layout_matrix = rbind(c(1, 2), c(1, 2)))


```
